---
title: "My dynamic report"
subtitle: "Daily Mobile Phone Usage"
author: "CAI WEI"
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

```

```{css}
body {
  font-family: "Segoe UI", "Helvetica Neue", sans-serif;
  line-height: 1.6;
  margin: 2em;
  background: #f7f9fc;
  color: #333;
}

h2 {
  border-left: 6px solid #4a90e2;
  padding-left: 10px;
  margin-top: 2em;
  color: #2c3e50;
}

p {
  font-size: 16px;
}
```

## Import data
```{r}
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQnXj1DqUHrhew5h86KAKoIVme16QkTopxrdBPqxsLJK3jh8_oreRlh4EB_29QU8w8AexFhFG2Dd5ze/pub?gid=1532890904&single=true&output=csv",header = TRUE)

latest_data <- logged_data %>%
  rename(
    usage_minutes = Q1..Approximately.how.many.minutes.did.you.spend.using.your.mobile.phone.today.,
    primary_activity = Q2..What.was.your.primary.phone.activity.today.,
    usage_location = Q3..Where.were.you.mostly.using.your.phone.today.,
    age_range = Q4..What.is.your.age.range.,
    productivity_score = Q5..On.a.scale.from.1.to.5..how.much.do.you.think.your.phone.use.affected.your.productivity.today.
  )

```

## Summary of Usage Time
```{r}
summary(latest_data$usage_minutes)
mean(latest_data$usage_minutes)
sd(latest_data$usage_minutes)
ggplot(latest_data, aes(x = usage_minutes)) +
  geom_histogram(binwidth = 100) +
  labs(title = "Distribution of Mobile Phone Usage Time",
       x = "Minutes per Day", y = "Count")
```

On average, participants used their phones for `r round(mean(latest_data$usage_minutes), 1) `minutes per day,
with a standard deviation of `r round(sd(latest_data$usage_minutes), 1)` minutes.

## Productivity Impact Score
```{r}
ggplot(latest_data, aes(x = as.factor(productivity_score))) +
  geom_bar() +
  labs(title = "Self-Reported Productivity Impact", x = "Score (1=Low, 5=High)", y = "Count")

```

The most common productivity scores were around 3 and 4, indicating a moderate level of impact from mobile phone usage.

## Most Common Phone Activities
```{r}
activity_data <- separate_rows(latest_data, primary_activity, sep = ", ")
ggplot(activity_data, aes(x = primary_activity)) +
  geom_bar() +
  coord_flip() +
  labs(title = "Most Common Primary Activities", x = "Activity", y = "Count")

```

Participants engaged in a wide variety of phone activities, with social media, messaging, and studying being the most common.

## Phone Usage Locations
```{r}
location_data <- separate_rows(latest_data, usage_location, sep = ", ")
ggplot(location_data, aes(x = usage_location)) +
  geom_bar() +
  labs(title = "Phone Usage Locations", x = "Location", y = "Count")
```

Most phone usage occurred at home, followed by use on public transport and in class.




